Structural and Geographic Influences on Residential Parking Availability in Toronto

### 2024-12-01 paper/paper.qmd
rendered paper

$$
\operatorname{logit}\left(\pi_i\right)=\alpha+\beta_1 \text { FrontYard}_i+\beta_2 \text { WidenedDriveway}_i+\gamma_1 \text { EtobicokeCentre}_i+\gamma_2 \text { ParkdaleHighPark}_i+\gamma_3 \text { TrinitySpadina}_i+\gamma_4 \text { YorkCentre}_i+ \\ \gamma_5 \text { YorkSouthWeston}_i+\gamma_6 \text { YorkWest}_i
$$

@@

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")
posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

@@

plot(first_model, "trace")

plot(first_model, "rhat")
```

@@

**Importance of Surveys and Sampling in Open Data**

>>>>

$$
\operatorname{logit}\left(\pi_i\right)=\alpha+\beta_1 \text { FrontYard}_i+\beta_2 \text { WidenedDriveway}_i+\gamma_1 \text { EtobicokeCentre}_i+\\\gamma_2 \text { ParkdaleHighPark}_i+\gamma_3 \text { TrinitySpadina}_i+\gamma_4 \text { YorkCentre}_i+ \\ \gamma_5 \text { YorkSouthWeston}_i+\gamma_6 \text { YorkWest}_i
$$

@@

pp_check(Bayesian_logit_model) +
  theme_classic() +
  theme(legend.position = "bottom")
posterior_vs_prior(Bayesian_logit_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

@@

plot(Bayesian_logit_model, "trace")

plot(Bayesian_logit_model, "rhat")
```

@@

## Overview of Survey Design
